\chapter*{Acknowledgements}
\vspace{7mm}
Bounteous praise for \textbf{``ALMIGHTY ALLAH''}, the magnificent, the merciful, the propitious, the supreme, the omnipotent, the omnipresent, the omniscient and sovereign whose blessing and glories flourish my thoughts and ambition and all the praises for the \textbf{``HOLY PROPHET MUHAMMAD (P.B.U.H.)''} for enlightening our conscience of faith in ALLAH, converging all His kindness and mercy upon him.

I feel much honor to express my deepest sense of gratitude and indebtedness to my honorable supervisor, \textbf{Dr. Muhammad Yaseen} (Assistant Professor), Department of Mathematics \& Statistics, University of Agriculture, Faisalabad from the core of my heart for his dynamic supervision, marvelous guidance, keen interest and encouraging behavior. With humble, profound and deepest sense of devotion I wish to record my sincere appreciation to \textbf{Mr. Muhammad Arif} (Lecturer), Department of Mathematics \& Statistics, University of Agriculture, Faisalabad and \textbf{Miss Madiha Ghamkhar} (Lecturer), Department of Mathematics and Statistics, University of Agriculture, Faisalabad for their sincere help, dynamic supervision and inspiring guidance throughout the course of this research work.

I want to express my great appreciation and sincerest gratitude to my friends and class fellows for their dexterous, dynamic, untiring help, friendly behavior and moral support during my whole study.

Last but not least, no acknowledgement could ever adequately express my obligation to my affectionate Parents and my brother \textbf{Sufian Khan} whose endless effort and best wishes sustained me at all stages of my life and encouraged me for achieving high ideas of life. May ALLAH bless all these people with long, happy and peaceful lives (Aameen)!
\begin{flushright}
\textbf{Umar Waqas Khan}
\end{flushright}
